`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-12-20 paper/paper.qmd
Fix a few formatting issues

We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in (Figure \ref{fig-autoplot-contacts}).

@@

`conmat` was built to predict at four settings: work, school, home, and other. 
One model is fitted for each setting. 
Each model fitted is a Poisson generalised additive model (GAM) with a log link function, which predicts the count of contacts, with an offset for the log of participants. 
The model has six covariates to explain key features of the relationship between ages, 
and two optional covariates for attendance at school or work.

@@

This code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling; @conway2023; @ryan2024].

>>>>

We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in Figure \ref{fig-autoplot-contacts}.

@@

`conmat` was built to predict at four settings: work, school, home, and other. 
One model is fitted for each setting. 
Each model fitted is a Poisson generalised additive model (GAM) with a log link function, which predicts the count of contacts, with an offset for the log of the number of participants. 
The model has six covariates to explain key features of the relationship between ages, 
and two optional covariates for attendance at school or work.

@@

The code underlying this software was used as a key input into several models for COVID-19 transmission and control in Australia and contributed to decisions around vaccination policy [@DohertyModelling; @conway2023; @ryan2024].
